---
title: My Final Project
---

## Motivation and Context

```{r}
#| label: do this first
#| echo: false
#| message: false

here::i_am("My_Final_Project.qmd")
```

This problem is particularly relevant to me because it provides an opportunity to explore the intersection of education and career outcomes, which is a key concern for many students, educators, and professionals alike. The factors that influence starting salaries after graduation have real-world implications, not only for students trying to plan their educational path but also for policymakers and educational institutions looking to improve the career prospects of graduates. Therefore, analyzing the relationship between academic performance and salary outcomes can show how education translates into financial success and helps both individuals and institutions make more informed choices.

This problem is also relevant to prospective students deciding which high school or university to attend, as well as universities and educators aiming to align their curricula with career success factors. Employers and recruiters may also find this analysis interesting, as it could offer insights into the predictive value of academic performance when hiring new graduates. In addition, this research could help policymakers and educational reformers understand if academic performance is a strong predictor of future earnings, which could inform discussions around education funding and access.

To understand the analysis, it is important to have some background in basic educational and career metrics. The concept of academic performance generally refers to measurable outcomes like a student's GPA (Grade Point Average), which reflects their grades and overall academic success. A high school GPA is an indicator of a student’s performance in secondary education, while a university GPA reflects academic success at the collegiate level. The SAT score is a standardized test score widely used in the U.S. to assess a student's readiness for college. These metrics are often seen as foundational indicators of a student's academic ability and can influence admission to universities and their academic standing once enrolled. Also, starting salary refers to the initial compensation a graduate receives when they enter the workforce. Understanding this requires knowledge of the economic context in which new graduates find themselves, including factors like job market conditions and industry-specific salary ranges. By analyzing these variables, I would like to explore whether higher academic performance correlates with a higher starting salary and whether it can serve as a predictor of financial success post-graduation.

On the other hand, while academic performance is a widely accepted measure of a student's capabilities, it may not be the sole factor influencing salary outcomes. Other elements such as internships, networking, or soft skills can also play significant roles in career success, and these factors may not always be reflected in academic scores.

## Main Objective

This project aims to explore how a student's academic performance, including high school GPA, SAT score, and university GPA, influences their starting salary after graduation, with the goal of identifying key academic factors that contribute to early career financial success.

## Packages Used In This Analysis

```{r}
#| label: load packages
#| message: false
#| warning: false

library(here)
library(readr)
library(dplyr)
library(ggplot2)
library(rsample)
library(recipes)
library(tidymodels)
library(glmnet)
library(naniar)
library(softImpute)
```

| Package | Use |
|--------------------------------|----------------------------------------|
| [here](https://github.com/jennybc/here_here) | to easily load and save data |
| [readr](https://readr.tidyverse.org/) | to import the CSV file data |
| [dplyr](https://dplyr.tidyverse.org/) | to massage and summarize data |
| [rsample](https://rsample.tidymodels.org/) | to split data into training and test sets |
| [ggplot2](https://ggplot2.tidyverse.org/) | to create nice-looking and informative graphs |


## Data Description

The data I am using for this project is from the "Education & Career Success" dataset available on Kaggle, a popular platform for sharing datasets. This dataset was created and updated by Adil Shamim, who designed it to explore the relationship between academic performance and career outcomes, such as starting salary and job offers. The dataset includes 5,000 records and covers variables such as high school GPA, SAT scores, university ranking, internships completed, and starting salary, among others. Although the dataset is synthetic, it was generated using real-world trends and data from education and career success studies. The primary purpose of this dataset is to allow users to conduct exploratory data analysis, create predictive models, and gain insights into factors influencing career success based on education. Particularly, the data is not directly gathered from real students, but is instead simulated based on existing trends to provide an accessible resource for data analysis.

```{r}
#| label: import data
#| warning: false

education_career_success <- readr::read_csv("education_career_success.csv")
```

### Data Limitations

While the "Education & Career Success" dataset offers a valuable resource for analyzing the impact of academic performance on career outcomes, there are several limitations when evaluating conclusions based on this data. One key limitation is that the dataset is synthetic, which means it may not fully reflect the complexities and variations found in real-world data. The data was generated based on existing trends, so it may miss nuances such as regional differences, socioeconomic factors, or the influence of specific industries on career outcomes. Additionally, there could be biases in how certain variables, like GPA or internships, are represented, which may not fully capture the diverse range of experiences students have in their academic or career paths.

Moreover, the dataset only includes a limited set of variables, which means that important factors influencing career success, such as personal networks, family background, or access to opportunities, are not directly measured. The soft_skills_score and networking_score are subjective ratings, which could introduce bias or inconsistencies in the data collection process. Also, the dataset's focus on a synthetic population means the conclusions drawn may not be fully generalizable to real-world populations. For example, the trends observed may not hold for different time periods, geographic locations, or industries. Finally, the dataset includes a "work-life balance" rating, which may vary significantly between companies or job types but is generalized across the entire dataset. These limitations should be carefully considered when drawing conclusions about the impact of academic performance on career success.

## Data Wrangling (Optional Section)

In this analysis, I plan to build a predictive model to explore the relationship between academic performance (such as high school GPA, SAT score, and university GPA) and career outcomes (such as starting salary). Since I am looking to build a model that can generalize to new, unseen data, it is essential to split the data into a training and test set. This will allow me to train the model on one subset of the data and then evaluate its performance on a separate, unseen subset. By doing this, I can assess how well the model generalizes to new data, helping to prevent overfitting (where the model performs well on the training data but poorly on unseen data).

I will use a standard approach for splitting the data, that is 80% of the data will be used for training, and 20% will be used for testing. This approach strikes a balance between having enough data to train the model while leaving enough data for evaluation. The data will be randomly shuffled to ensure that the split is representative of the overall dataset.

```{r}
#| label: split data into training and test set
set.seed(195)
n <- nrow(education_career_success)
train_indices <- sample(n, size = floor(0.8*n))
ECS_train <- education_career_success[train_indices,]
ECS_test <- education_career_success[-train_indices,]
```

```{r}
#| label: check how much missing data is present
education_career_success |>
  miss_var_summary()
```

-   The result shows that there is no missing data in the original dataset.

## Exploratory Data Analysis

-   First, I will check if `Starting_Salary` has unusual values or not

```{r}
#| label: check unusual values for Starting_Salary
# Since `Starting_Salary` is described as First job salary in USD ($25,000 - $150,000)
unusual_start_salary <- ECS_train %>% filter(`Starting_Salary` < 25000 | `Starting_Salary` > 150000)
unusual_start_salary
```

The result shows that `Starting_Salary` has no unusual values.

-   Then, I will explore the distribution of my response variable, `Starting_Salary`

```{r}
#| label: describe the basic statistics of Starting_Salary
ECS_train |>
  summarize(
    num_total = n(),
    mean = mean(Starting_Salary, na.rm = TRUE),
    sd = sd(Starting_Salary, na.rm = TRUE),
    min = min(Starting_Salary, na.rm = TRUE),
    Q1 = quantile(Starting_Salary, 0.25, na.rm = TRUE),
    median = median(Starting_Salary, na.rm = TRUE),
    Q3 = quantile(Starting_Salary, 0.75, na.rm = TRUE),
    max = max(Starting_Salary, na.rm = TRUE),
    IQR = IQR(Starting_Salary, na.rm = TRUE)
  )
```

```{r}
#| label: explore the distribution of Starting_Salary
ggplot(data = ECS_train,
       mapping = aes(
         x = Starting_Salary
         )
       ) + 
  geom_histogram(center = 65000, binwidth = 10000) +
  labs(title = "Histogram of Starting_Salary", x = "Starting_Salary")
```

Based on the summary and histogram, the `Starting_Salary` distribution shows that most graduates earn between $\$40,000$ and $\$60,000$, with a few making much higher salaries, up to $\$101,000$. Since the median is lower than the mean $(\$50,400 < \$50,620)$, the salaries are slightly right-skewed, with more people earning on the lower end of the scale and fewer reaching the high salary levels, indicating that a small number of people have very high-paying jobs.

-   Second, I will check if `High_School_GPA` has unusual values or not

```{r}
#| label: check unusual values for High_School_GPA
# Since `High_School_GPA` is on the scale 2.0 - 4.0
unusual_high_scho_GPA <- ECS_train %>% filter(`High_School_GPA` < 2 | `High_School_GPA` > 4)
unusual_high_scho_GPA
```

The result shows that `High_School_GPA` has no unusual values.

-   Then, I will explore the distribution of `High_School_GPA`

```{r}
#| label: describe the basic statistics of High_School_GPA
ECS_train |>
  summarize(
    num_total = n(),
    mean = mean(High_School_GPA, na.rm = TRUE),
    sd = sd(High_School_GPA, na.rm = TRUE),
    min = min(High_School_GPA, na.rm = TRUE),
    Q1 = quantile(High_School_GPA, 0.25, na.rm = TRUE),
    median = median(High_School_GPA, na.rm = TRUE),
    Q3 = quantile(High_School_GPA, 0.75, na.rm = TRUE),
    max = max(High_School_GPA, na.rm = TRUE),
    IQR = IQR(High_School_GPA, na.rm = TRUE)
  )
```

```{r}
#| label: explore the distribution of High_School_GPA
ggplot(data = ECS_train,
       mapping = aes(
         x = High_School_GPA
         )
       ) + 
  geom_histogram(center = 3, binwidth = 0.1) +
  labs(title = "Histogram of High_School_GPA", x = "High_School_GPA")
```

Based on the summary and histogram, the `High_School_GPA` distribution is fairly centered around a 3.0 average, with most students scoring between 2.5 and 3.5, indicating a fairly typical "B" to "B+" performance. It is roughly uniform with no extreme outliers. Since the standard deviation is 0.577, the data is fairly consistent with moderate variability.

-   Third, I will check if `SAT_Score` has unusual values or not

```{r}
#| label: check unusual values of SAT_Score
# Since `SAT_Score` is described as Standardized test score (900 - 1600)
unusual_SAT_score <- ECS_train %>% filter(`SAT_Score` < 900 | `SAT_Score` > 1600)
unusual_SAT_score
```

The result shows that `SAT_Score` has no unusual values.

-   Then, I will explore the distribution of `SAT_Score`

```{r}
#| label: describe the basic statistics of SAT_Score
ECS_train |>
  summarize(
    num_total = n(),
    mean = mean(SAT_Score, na.rm = TRUE),
    sd = sd(SAT_Score, na.rm = TRUE),
    min = min(SAT_Score, na.rm = TRUE),
    Q1 = quantile(SAT_Score, 0.25, na.rm = TRUE),
    median = median(SAT_Score, na.rm = TRUE),
    Q3 = quantile(SAT_Score, 0.75, na.rm = TRUE),
    max = max(SAT_Score, na.rm = TRUE),
    IQR = IQR(SAT_Score, na.rm = TRUE)
  )
```

```{r}
#| label: explore the distribution of SAT_Score
ggplot(data = ECS_train,
       mapping = aes(
         x = SAT_Score
         )
       ) + 
  geom_histogram(center = 1200, binwidth = 50) +
  labs(title = "Histogram of SAT_Score", x = "SAT_Score")
```

Based on the summary and histogram, the SAT scores are fairly evenly spread around an average score of about 1253. There is moderate variability in scores, with most students scoring between 1074 and 1432, and a few students with perfect scores of 1600. The distribution appears balanced and doesn’t have any extreme outliers.

-   Finally, I will check if `University_GPA` has unusual values or not

```{r}
#| label: check unusual values of University_GPA
# Since `University_GPA` is on the scale 2.0 - 4.0
unusual_uni_GPA <- ECS_train %>% filter(`University_GPA` < 2 | `University_GPA` > 4)
unusual_uni_GPA
```

The result shows that `University_GPA` has no unusual values.

-   Then, I will explore the distribution of `University_GPA`

```{r}
#| label: describe the basic statistics of University_GPA
ECS_train |>
  summarize(
    num_total = n(),
    mean = mean(University_GPA, na.rm = TRUE),
    sd = sd(University_GPA, na.rm = TRUE),
    min = min(University_GPA, na.rm = TRUE),
    Q1 = quantile(University_GPA, 0.25, na.rm = TRUE),
    median = median(University_GPA, na.rm = TRUE),
    Q3 = quantile(University_GPA, 0.75, na.rm = TRUE),
    max = max(University_GPA, na.rm = TRUE),
    IQR = IQR(University_GPA, na.rm = TRUE)
  )
```

```{r}
#| label: explore the distribution of University_GPA
ggplot(data = ECS_train,
       mapping = aes(
         x = University_GPA
         )
       ) + 
  geom_histogram(center = 3, binwidth = 0.05) +
  labs(title = "Histogram of University_GPA", x = "University_GPA")
```

Based on the summary and histogram, the `University_GPA` distribution is fairly uniform, with most students earning GPAs between 2.52 and 3.52, and an average GPA of around 3.02. The distribution is relatively consistent, with no extreme outliers, and the spread is moderate, suggesting most students perform similarly in university.

-   Investigate the association between the two variables.

-   First, I will investigate the association between `High_School_GPA` and `Starting_Salary`by creating a scatterplot to show the relationship between these two variables and see if they have a linear relationship.

```{r}
ggplot(data = ECS_train,
       mapping = aes(
         x = High_School_GPA,
         y = Starting_Salary
         )
       ) +
  geom_point(size = 0.8) +
  labs(title = "High_School_GPA vs. Starting_Salary", 
       x = "High_School_GPA",
       y = "Starting_Salary") +
  geom_smooth(method = "loess", se = FALSE)

```

Based on the scatterplot, there appears to be no significant relationship between `High_School_GPA` and `Starting_Salary`. The plot does not exhibit any clear trend, and the blue regression line is nearly horizontal, suggesting that `High_School_GPA` does not have a meaningful effect on `Starting_Salary` across its range."

To double check, I calculate the correlation coefficient between two variables.

```{r}
#| label: calculate the correlation coefficient between High_School_GPA and Starting_Salary 
cor(ECS_train$Starting_Salary, ECS_train$High_School_GPA)
```

We see that the correlation coefficient is very small (0.002), which means that there is no clear relationship between `High_School_GPA` and `Starting_Salary`.

-   Next, I will investigate the association between `SAT_Score` and `Starting_Salary` by creating a scatterplot to show the relationship between these two variables and see if they have a linear relationship.

```{r}
ggplot(data = ECS_train,
       mapping = aes(
         x = SAT_Score,
         y = Starting_Salary
         )
       ) +
  geom_point(size = 0.8) +
  labs(title = "SAT_Score vs. Starting_Salary", 
       x = "SAT_Score",
       y = "Starting_Salary") +
  geom_smooth(method = "loess", se = FALSE)
```

Based on the scatterplot, it looks like there is no relationship between `SAT_Score` and `Starting_Salary` because this plot does not show any specific trend, and the blue line seems to be horizontal across different values of `SAT_Score`.

To double check, I calculate the correlation coefficient between two variables.

```{r}
#| label: calculate the correlation coefficient between SAT_Score and Starting_Salary
cor(ECS_train$Starting_Salary, ECS_train$SAT_Score)
```

Since the correlation coefficient is close to 0 (0.001), there is no relationship between `SAT_Score` and `Starting Salary`.

-   Then, I will investigate the association between `University_GPA` and `Starting_Salary`by creating a scatterplot to show the relationship between these two variables and see if they have a linear relationship.

```{r}
ggplot(data = ECS_train,
       mapping = aes(
         x = University_GPA,
         y = Starting_Salary
         )
       ) +
  geom_point(size = 0.8) +
  labs(title = "University_GPA vs. Starting_Salary", 
       x = "University_GPA",
       y = "Starting_Salary") +
  geom_smooth(method = "loess", se = FALSE)

```

Based on the scatterplot, it does not have any detectable trend, and the blue regression line is nearly horizontal. This indicates that `University_GPA` is not significantly associated with `Starting_Salary`.

To double check, I calculate the correlation coefficient between two variables.

```{r}
#| label: calculate the correlation coefficient between University_GPA and Starting_Salary
cor(ECS_train$Starting_Salary, ECS_train$University_GPA)
```

Since the correlation coefficient is close to 0 (-0.01), there is no significant relationship between `University_GPA` and `Starting_Salary`.

Through exploratory data analysis, I examined the relationships between starting salary and various academic factors, including high school GPA, SAT score, and university GPA. Surprisingly, the analysis revealed that none of these factors showed a meaningful relationship with starting salary. The correlation coefficients for high school GPA, SAT score, and university GPA were very close to zero, indicating weak or no linear associations with starting salary. Additionally, visual inspections of the data, such as scatterplots and regression lines, showed no discernible trends.

This finding suggests that academic performance, as measured by these variables, may not be strong predictors of early career financial success in this dataset. However, this does not necessarily mean that academic factors are unimportant in determining starting salary in general. Other factors not explored in this analysis, such as internships, networking, or soft skills, may play a more significant role in shaping starting salaries. Further research could investigate these other variables to provide a more comprehensive understanding of the factors influencing early career earnings.

## Modeling

I selected linear regression as the primary modeling technique for this analysis because it is a fundamental, interpretable method well-suited for examining the relationship between one or more predictor variables and a continuous response variable, such as Starting_Salary. This approach estimates the effect of each independent variable by fitting a line that minimizes the sum of squared residuals between observed and predicted values. Linear regression is particularly appropriate here because it enables us to quantify the marginal effect of each academic variable on predicted salary, provides directly interpretable coefficients (e.g., an additional SAT point corresponds to a specific increase in salary), and assumes a linear relationship that aligns—albeit weakly—with patterns observed during exploratory analysis.

Before fitting the model, I center and scale the numeric predictors to ensure comparability of the coefficients and avoid issues of variable scale.

```{r}
# Build a recipe to preprocess data
salary_recipe <- recipe(Starting_Salary ~ High_School_GPA + SAT_Score
                        + University_GPA,
                        data = ECS_train) |>
  step_normalize(all_predictors())  # Standardize predictors

# Define linear regression model
lm_model <- linear_reg() |>
  set_engine("lm") |>
  set_mode("regression")

# Create workflow
lm_workflow <- workflow() |>
  add_model(lm_model) |>
  add_recipe(salary_recipe)

# Fit the model
lm_fit <- fit(lm_workflow, data = ECS_train)
```

To evaluate the performance of the model, I use two key metrics: Root Mean Squared Error (RMSE), which measures the average magnitude of prediction errors, and R-squared (the Coefficient of Determination), which indicates the proportion of variance in the response variable explained by the model.

```{r}
# Predict on the test set
test_predictions <- predict(lm_fit, new_data = ECS_test) |>
  bind_cols(ECS_test)

# Calculate performance metrics
lm_metrics <- test_predictions |>
  metrics(truth = Starting_Salary, estimate = .pred)

lm_metrics
```

The predictive modeling analysis reveals that the academic factors considered `High_School_GPA`, `SAT_Score`, and `University_GPA` do not significantly predict `Starting_Salary`. The model's performance metrics, including a very low R-squared value (0.0017) and high RMSE ($\${14,550.38}$), indicate that these variables account for very little of the variability in starting salaries. 

```{r}
# Lasso model
lasso_model <- linear_reg(penalty = tune(), mixture = 1) |> 
  set_engine("glmnet") |> 
  set_mode("regression")

# Create workflow
lasso_workflow <- workflow() |>
  add_model(lasso_model) |>
  add_recipe(salary_recipe)

# 5-fold cross-validation
set.seed(195)
cv_folds <- vfold_cv(ECS_train, v = 5)

# Grid of penalty values (log scale)
penalty_grid <- grid_regular(penalty(), levels = 30)

# Tune the model
lasso_tune_results <- tune_grid(
  lasso_workflow,
  resamples = cv_folds,
  grid = penalty_grid,
  metrics = metric_set(rmse, rsq, mae)
)
```

```{r}
# Plot RMSE vs lambda
lasso_tune_results |>
  collect_metrics() |>
  filter(.metric == "rmse") |>
  ggplot(mapping = aes(x = penalty, y = mean)) + geom_point() + geom_line() +
  scale_x_log10() +
  labs(title = "RMSE vs Lambda (log scale)", x = "Lambda (penalty)", y =
         "Mean RMSE")
```

```{r}
show_best(lasso_tune_results, metric = "rmse", n = 1) # best lambda value based on the lowest RMSE
```

```{r}
lasso_best <- lasso_tune_results |>
  select_by_one_std_err(
    metric = "rmse",
    desc(penalty) # order penalty from largest (highest bias = simplest model) to smallest
)
lasso_best
```

```{r}
# Finalize the workflow with the best penalty
final_lasso_workflow <- lasso_workflow |>
  finalize_workflow(parameters = lasso_best)

# Fit the finalized model to the training data
final_lasso_fit <- final_lasso_workflow |>
  fit(data = ECS_train)
final_lasso_fit
```

```{r}
# Predict on the test set
lasso_preds <- broom::augment(final_lasso_fit, new_data = ECS_test)
```

```{r}
# Evaluate model performance
lasso_metrics <- lasso_preds |> 
  metrics(truth = Starting_Salary, estimate = .pred)

lasso_metrics
```

The Lasso regression model yielded performance metrics that are nearly identical to those of the earlier linear regression model, with an RMSE of approximately $\${14,550}$, an MAE of around $\${11,909}$, and a very low R-squared value of $0.0017$. These results indicate that the inclusion of regularization did not improve the model's predictive ability, and the selected academic variables `High_School_GPA`, `SAT_Score`, and `University_GPA` still explain virtually none of the variation in starting salary. This reinforces the conclusion that these academic metrics alone are not strong predictors of early career financial outcomes in this dataset.

In this analysis, both the multiple linear regression and Lasso regression models were used to examine whether academic performance, which is measured by high school GPA, SAT score, and university GPA, could predict starting salary after graduation. The results from both models were nearly identical, with very low R-squared values (around 0.0017) and relatively high RMSE values (approximately \$14,550). These outcomes indicate that academic metrics alone explain virtually none of the variation in starting salary within this dataset. Even after applying regularization through Lasso, model performance did not improve, suggesting that the predictors used lack meaningful association with the outcome variable. This highlights a key limitation of the dataset, which is both synthetic and overly simplified. It also reinforces the importance of incorporating other real-world factors such as internships, work experience, networking, or soft skills when modeling career outcomes. Without these, academic performance alone appears insufficient as a predictor of early career financial success.

## Insights

```{r}
# Create a data frame summarizing both models' performance
model_metrics <- tibble(
  Model = c("Linear Regression", "Lasso Regression"),
  RMSE = c(14550.38, 14550.30),
  MAE = c(11909.44, 11909.37),
  R_squared = c(0.0017, 0.0017)
)
model_metrics
```

After conducting both linear regression and Lasso regression models using `High_School_GPA`, `SAT_Score`, and `University_GPA` as predictors, the primary insight from this analysis is that these academic metrics have very limited predictive power for determining `Starting_Salary`. As illustrated in the performance comparison table above, both models produced nearly identical results, with RMSE values around $\${14,550}$ and R-squared values close to $0$. This indicates that the models could not explain any meaningful variation in starting salaries using these academic factors. The finding was further supported by the near-zero correlation coefficients and flat trend lines observed in scatterplots between each academic variable and starting salary. This suggests that, at least within this dataset, early career financial outcomes are likely influenced by other variables not included in the initial models such as internships, soft skills, or professional networking, which should be explored in future analyses.

### Limitations and Future Work

There are several key limitations that affect the reliability and generalizability of the modeling results in this project. First, the models consistently performed poorly across all evaluation metrics ($R^2 \approx 0.0017$), meaning that they failed to meaningfully predict starting salaries for almost all individuals in the dataset. This suggests that starting salaries are influenced by factors not captured in the academic variables used, and that the model is particularly weak for students across the board whether high or low achieving because it lacks relevant predictors such as internships, job field, networking, or soft skills.

A major limitation lies in the nature of the dataset itself, which is synthetic and not based on actual student or employment records. As a result, the relationships between variables do not always reflect real-world patterns. For example, `High_School_GPA` and `University_GPA` have very similar, overly uniform distributions, which is unrealistic; in reality, University GPA tends to be more tightly clustered, and often correlates with earlier academic performance. Additionally, SAT scores are suspiciously centered and lack the expected skewness seen in real testing data. These issues likely distort any potential predictive relationships and limit the realism of the analysis.

The modeling methods used including linear regression and Lasso regression, which rely on certain assumptions, including linearity and the meaningfulness of the input features. Since the features used lack strong theoretical or empirical justification in this dataset, the assumptions behind these methods are weakly supported, which further undermines the model's validity. Moreover, while regularization helps with overfitting, it cannot fix fundamentally poor data quality or irrelevant features.

From an ethical standpoint, while the data is simulated and anonymized, there are still considerations about how such analysis could be interpreted. For example, using academic performance to predict salary outcomes might unintentionally reinforce meritocratic assumptions that overlook systemic inequalities in access to education or professional opportunities. In the real world, decisions based on such limited models could unfairly disadvantage individuals whose strengths lie outside standardized academic metrics.

To improve this analysis in the future, better data collection is essential, ideally using real, anonymized graduate outcome surveys that include richer variables: major or field of study, internship experience, job sector, geographic location, and demographic background. With more realistic and complete data, a wider range of modeling approaches such as tree-based models or mixed-effects models could be explored with more confidence in the results.

### Reflection (Optional Subsection)
